---
title: "What are the Cowboyest Names in Switzerland?"
subtitle: "Data Management and Integration Assignment"
author: "Marius Furter and Morley J Weston"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(tidyverse)
library(DBI)
library(knitr)
```

# Create the database
```{r}
conn <- dbConnect(RSQLite::SQLite(), "cowboys.db")
```

# Population by Commune

The data was gathered from the Swiss federal geodata portal at data.geo.admin.ch,
and converted from an ESRI shapefile into a CSV in QGIS.
```{r message=FALSE}
communes <- read_csv("input_data/gemeinde.csv")
communes <- communes %>% 
  filter(!is.na(EINWOHNERZ)) %>%
  select(BFS_NUMMER, EINWOHNERZ, NAME)

communes %>% sample_n(10) %>% kable()
```

We created a table for the communes with the unique ID as a primary key ...
```{r}
dbExecute(conn, "
  create table if not exists communes (
    commune_id int primary key,
    population int,
    name text
  )          
")
```

```{r}
for (i in 1:nrow(communes)) {
  row = communes[i,]
  dbExecute(conn, "
            insert into communes (commune_id, population, name)
            values (?, ?, ?)",
          params = c(row$BFS_NUMMER, row$EINWOHNERZ, row$NAME))
}
```

```{r}
dbGetQuery(conn, "select * from communes limit 10") %>% kable()
```



# Cattle population per commune
```{r message=FALSE}
cattle_population <- read_delim("input_data/cattle-map-commune.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)
cattle_population <- cattle_population %>% 
  select(MunicipalityNumber, count)

cattle_population %>% sample_n(10) %>% kable()
```






TODO: 
1. alter table communes to add a cattle_population column, 
2. update communes cattle_population where commune_id is equal

www.sqlitetutorial.net is a good resource




# Most common family names by commune
```{r message=FALSE}
family_names <-
  read_delim(
    "input_data/family-names-commune.csv",
    delim = ";",
    escape_double = FALSE,
    trim_ws = TRUE
  )
family_names <- family_names %>% 
  filter(TIME_PERIOD == 2021) %>% 
  filter(RANG_GDE <= 3) %>% 
  select(LASTNAME, GDENR, RANG_GDE, VALUE)

family_names %>% sample_n(10) %>% kable()
```

```{r}
dbExecute(conn, "
  create table if not exists family_names (
    id integer primary key,
    name text,
    commune_id int,
    name_count int,
    rank int,
    foreign key(commune_id) references communes(commune_id)
  )          
")
```


```{r}
pb = txtProgressBar(min = 1, max = nrow(family_names), initial = 1) 

for (i in 1:nrow(family_names)) {
  row = family_names[i,]
  dbExecute(conn, "
            insert into family_names (name, commune_id, name_count, rank)
            values (?, ?, ?, ?)",
          params = c(row$LASTNAME, row$GDENR, row$VALUE, row$RANG_GDE))
  
  if (i %% 100 == 0) {
    setTxtProgressBar(pb,i)} 
}
close(pb)
```

```{r}
dbGetQuery(conn, "select * from family_names limit 10") %>% kable()
```

# Most common cattle names by commune
```{r message=FALSE}
cattle_NamesFemaleCalves <- read_delim("input_data/cattle-NamesFemaleCalves.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE) %>%
  mutate(sex="F")

cattle_NamesMaleCalves <- read_delim("input_data/cattle-NamesMaleCalves.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE) %>% 
  mutate(sex="M")

cattle_names <- bind_rows(cattle_NamesFemaleCalves, cattle_NamesMaleCalves)
rm(cattle_NamesFemaleCalves, cattle_NamesMaleCalves)

cattle_names <- cattle_names %>% 
  filter(year==2022) %>% 
  filter(OwnerLanguage != "__all__") %>% 
  select(Name, count, Rank, sex, OwnerLanguage)

cattle_names %>% arrange(Rank, sex, OwnerLanguage) %>% head(10) %>% kable()
```






# TODO make table for this






